\begin{abstract}
	\indent In this digitalization era, the level of community needs for information is increasing. This make exchanging the information very easy. This makes the sensitive information leakage to the unauthorized party. The leakage of information divided into 2 when viewed from the integrity of information they get. First they get all information or second they only get a partial of information. Partial information leakage, make unauthorized party to reconstruct the information they get from all piece information they have already obtain.
\\
\indent The problem in this undergraduate thesis book is the problem to get plaintext as much as possible from the ciphertext and upper bound of key length. The encryption method is using the Vigenere Cipher technique. Given the plaintext and ciphertext, but there is missing information in both of them. Given the upper bound of key length, that is not real key length. To reconstruct plaintext from piece information, must find the length of key from modify Kasiski Examination and Intersection. Some things to note that using only modify Kasiski Examination and Intersection can not solving the problem. Required to optimize both of them to get the answer and right time.
\\
\indent The results show that this problem is successfully solved. Averaging time of 4.42 second and averaging memory use about 26.5MB to solve 2MB data.
\\
\noindent \textbf{Keywords}: \textit{Ciphertext}, \textit{Kasiski Examination}, \textit{Optimization},\textit{Plaintext}.
\end{abstract}